Is it time for an NBA expansion?

### 2024-04-12 paper/paper.qmd
Tried Rendering

# creating table for league average
nba_data <- full_nba_data %>% 
  filter(Team == "League Average")

write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE)
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE)
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

#creating table for league average
nba_data <- full_nba_data %>% 
  filter(Team == "League Average")

#saving Clean Data
write.csv(nba_data, "../data/clean_data/nba_data.csv", row.names = FALSE)
write.csv(full_nba_data, "../data/clean_data/full_nba_data.csv", row.names = FALSE)
```

@@

@@
